# Reproducible Research: Peer Assessment 1

## Loading and preprocessing the data
1. Load the data (i.e. read.csv())
2. Process/transform the data (if necessary) into a format suitable for your analysis
```{r}
library(xtable)
data <- read.csv("activity.csv")
```

Summary of the Raw Data
```{r}
summary(data)
str(data)
```


## What is mean total number of steps taken per day? 
For this part of the assignment, you can ignore the missing values in the dataset.
```{r}
data <- data[complete.cases(data),]
```

- Make a histogram of the total number of steps taken each day
```{r, fig.height=8, fig.width=10}
  stepsInDays <- aggregate(data$steps,list(date = data$date), sum)
  plot(x=stepsInDays[,1],y=stepsInDays[,2],type="h",main ="Number of Steps Per day",
       xlab = "Date",ylab="Number of Steps")
```

- Calculate and report the mean and median total number of steps taken per day
```{r}
  daysMean <- aggregate(data$steps,list(date = data$date), mean)
  daysMedian <- aggregate(data$steps,list(date = data$date), median)
  mmtable <- cbind(daysMean,daysMedian[,2])
  names(mmtable) <- c("Date","Mean","Median")
  mmtable 
```
## What is the average daily activity pattern?
- Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r}
stepsPerInterval <- aggregate(data$steps,list(interval = data$interval), mean)
plot(x=stepsPerInterval[,1],y=stepsPerInterval[,2],type="l",main ="Average Number of Steps",
       xlab = "Interval",ylab="Average")
```
- Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?
```{r}
  MaxNumberofSteps <- with(stepsPerInterval,interval[x==max(x)])
```

- **Answer :** Max Number of Steps is in interval **`r MaxNumberofSteps`**.

## Imputing missing values



## Are there differences in activity patterns between weekdays and weekends?
